Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
adding comment in Sec 3.1.

    sol: this paragraph still has issues
    \begin{itemize}
        \item test discovery is not an aspect of BDD, but an emphasis
            on automating things, so that they e.g. work with CI is.
        \item @mkl your previous version stated, that BDD includes
            other things (ATDD!), but we only focus on TDD.  I think
            this got lost.
    \end{itemize}

@@

Hspec is thus useful for \emph{code documentation} but we observed that parts
of a specification can be useful as user documentation. To that end, we think
Python's {\tt doctest} module~\cite{doctest} is interesting.
It is not commonly described as a BDD tool, but we think it can be
used for BDD.
There is a Haskell version called Doctest\footnote{%
http://hackage.haskell.org/package/doctest}, which is integrated with Haddock~\cite{haddock},
the standard documentation mechanism for Haskell.
It extracts \emph{interactive examples} in Haddock comments and
verify them automatically.

@@

>>>>

    sol: this paragraph still has issues
    \begin{itemize}
        \item test discovery is not an aspect of BDD, only an emphasis
            on automating things is an aspect of BDD, so that thing
            e.g. work with CI.
        \item @mkl your previous version stated, that BDD includes
            other things (ATDD!), but we only focus on TDD.  I think
            meaning got lost now.
    \end{itemize}

@@

Hspec is thus useful for \emph{code documentation} but we observed that parts
of a specification can be useful as user documentation. To that end, we think
Python's {\tt doctest} module~\cite{doctest} is interesting.
It is not commonly described as a BDD tool, but we think it can be
used for BDD.
There is a Haskell version called Doctest\footnote{%
http://hackage.haskell.org/package/doctest}, which is integrated with Haddock~\cite{haddock},
the standard documentation mechanism for Haskell.
It extracts \emph{interactive examples} from Haddock comments and
verifies them automatically.

@@

\begin{quote}
    \emph{kazu: I would like to add the following:}

So, we need common syntax to describe examples and properties
independently in Haddock. Doctest should automatically verify
examples and test properties.
\end{quote}
